On Sample Size Needed for Block Bootstrap Confidence Intervals to Have Desired Coverage Rates

### 2023-09-01 Manuscript/manuscript.tex
added true values of lag-1 autocorr
Responded to Commit

The series were generated by marginally transforming the
AR(1) series  $X_t$in the simulation study by
\begin{equation*}
W_t = F^{-1}[\Phi(X_t)],
\end{equation*}
where $F^{-1}(p)$ is the quantile function for the unit exponential 
distribution. The true mean and standard deviation parameters are~1. The lag-1
autocorrelation coefficient is not invariant to the
transformation\citep{hofert2018ealements}, but its value can be obtained by
\begin{equation*}
\int_\infty^\infty \int_\infty^\infty F^{-1}[\Phi(x)] F^{-1}[\Phi(y)] g_2(x, y; \phi) \dd x \dd y - 1,
\end{equation*}
where $g_2(x, y; \phi)$ is the density of a standard bivariate normal
distribution with correlation~$\phi$. We kept the configuration of
$\phi \in \{-0.4, -0.2, 0.0, 0.2, 0.4\}$.

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{figures/plot_exp_mu}
  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
    the marginal mean $\mu$ of a marginally transformed AR(1) process with AR 
    coefficient
    $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ with an 
    underlying exponential distribution ($\lambda = 1$) and series length
    $n \in \{100, 200, 400, 800, 1600, 3200\}$ with
    an exponential distribution with $\lambda = 1$ based on 10,000 replicates. 
    The error bars represent 95\% CIs of the real coverage rates.}
  \label{fig:exp_mu}
\end{figure}

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{figures/plot_exp_sigma}
  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
    the marginal standard deviation $\sigma_x$ of a marginally transformed AR(1) 
    process with AR 
    coefficient $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ with an 
    underlying exponential distribution ($\lambda = 1$) and series length 
    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates. 
    The error bars represent 95\% CIs of the real coverage rates.}
  \label{fig:exp_sigma}
\end{figure}

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{figures/plot_exp_phi}
  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for 
    the first-order autocorrelation coefficient $\phi$ of a marginally 
    transformed AR(1) process with
    $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ with 
    an 
    underlying exponential distribution ($\lambda = 1$) and series length
    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates. 
    The error bars represent 95\% CIs of the real coverage rates.}
  \label{fig:exp_phi}
\end{figure}

@@

\jy{change the captions of the other three figures accordingly}

>>>>

The series were generated by marginally transforming the
AR(1) series  $X_t$ in the simulation study by
\begin{equation*}
W_t = F^{-1}[\Phi(X_t)],
\end{equation*}
where $F^{-1}(p)$ is the quantile function for the unit exponential 
distribution. The true mean and standard deviation parameters are~1. The lag-1
autocorrelation coefficient is not invariant to the
transformation, \citep{hofert2018elements} but its value can be obtained by
\begin{equation*}
\int_{-\infty}^\infty \int_{-\infty}^\infty F^{-1}[\Phi(x)] F^{-1}[\Phi(y)] g_2(x, y; \phi) \dd x \dd y - 1,
\end{equation*}
where $g_2(x, y; \phi)$ is the density of a standard bivariate normal
distribution with correlation~$\phi$. We kept the configuration of
$\phi \in \{-0.4, -0.2, 0.0, 0.2, 0.4\}$, and the corresponding lag-1
autocorrelation coefficients are $\{-0.298, -0.156, 0, 0.170, 0.355\}$.

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{figures/plot_exp_mu}
  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
    the marginal mean $\mu$ of a stationary series with marginal exponential
    distribution obtained by transforming an AR(1) process with
    $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ with series length
    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates. 
    The error bars represent 95\% CIs of the real coverage rates.}
  \label{fig:exp_mu}
\end{figure}

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{figures/plot_exp_sigma}
  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
    the marginal standard deviation $\sigma_x$ of a stationary series with 
    marginal exponential distribution obtained by transforming an AR(1) process
    with $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ with series length 
    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates. 
    The error bars represent 95\% CIs of the real coverage rates.}
  \label{fig:exp_sigma}
\end{figure}

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{figures/plot_exp_phi}
  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for 
    the first-order autocorrelation coefficient $\phi$ of a stationary series
    with marginal exponential distribution obtained by transforming an AR(1) 
    process with 
    $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ with series length
    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates. 
    The error bars represent 95\% CIs of the real coverage rates.}
  \label{fig:exp_phi}
\end{figure}

@@

\jy{change the captions of the other three figures accordingly}
\mc{addressed}
